\documentclass[paper=a4,fontsize=11pt]{article} % KOMA-article class

\usepackage[english]{babel}     % Language
\usepackage{amsmath}
\usepackage{fontspec}
\usepackage{xcolor}

\usepackage{enumitem}           % For eliminating white space for itemize
\usepackage{nopageno}           % Get rid of page number

\usepackage[margin=0.5cm]{geometry} % Set margins

\setmainfont{Calibri}

\def \lineThickness {1pt}               % Line thickness for separating
\def \nameColWidth {0.66\textwidth}		% Name column width
\def \mainColWidth {0.8\textwidth}		% Main column width
\def \leftColWidth {0.125\textwidth}		% Left column width

\allowdisplaybreaks

\begin{document}
	\setlength{\abovedisplayskip}{0pt}
	\setlength{\belowdisplayskip}{0pt}
	\setlength{\abovedisplayshortskip}{0pt}
	\setlength{\belowdisplayshortskip}{0pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{align*}
	&
	\begin{array}{ll}
	\parbox[t]{0.55\textwidth}{%
		\text{\fontsize{40}{48}\selectfont \ \textbf{Pavlo Vlastos}}\\
%		\text{\ Electrical and Computer Engineer}
	}%
	&
	\parbox{\mainColWidth}{%
		$\begin{array}[t]{ll}
		\textbf{Email:} & \text{pvlastos@ucsc.edu, pavlogv@gmail.com}\\
		\textbf{LinkedIn:} & \text{linkedin.com/in/pavlo-vlastos}\\
		\textbf{Location:} & \text{Santa Cruz, California}\\
		\textbf{Website:} & \text{www.pavl.org}\\
		\textbf{GPA:} & \textbf{4.0 PhD} \ \text{(3.3 Prior)}
		\end{array}$
	}%
	\end{array}
\end{align*}
\begin{align*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\colorbox{black}{\color{white}{
			\parbox[t]{\leftColWidth}{%
				\textbf{Education}}
			}%
		}
		& &
		\parbox[t]{\mainColWidth}{%
			\textbf{PhD in Computer Engineering} \hfill \textbf{September 2017 - January 2022} \\
			Emphasis in Robotics and Control Theory\\
			University of California, Santa Cruz
			\begin{itemize}[noitemsep,topsep=0pt]
			\item Courses in robotics, MAV Aerodynamics, control theory, attitude estimation, and embedded programming.
			\item Research: Developing low-cost ASVs for oceanography. 
			\item Conducting validation of Complementary Filter-based AHRS.
			\end{itemize}
			\textbf{B.S. in Robotics Engineering} \hfill \textbf{September 2013 - June 2017}\\
			University of California, Santa Cruz
			\begin{itemize}[noitemsep,topsep=0pt]
			\item Courses in mechatronics, applied linear algebra, and feedback control.
			\end{itemize}
		}%
	\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\colorbox{black}{\color{white}{
				\parbox[t]{\leftColWidth}{%
					\textbf{Work Experience}}
			}%
		}
		& &
		\parbox[t]{\mainColWidth}{%
			\textbf{NASA} Ames \hfill \textbf{June 2021 - September 2021}\\
			\quad Engineering Intern (SJSU Research Foundation and KBR)
			\begin{itemize}[noitemsep,topsep=0pt]
				\item Integrated Real-Time Location System (RTLS) with real-time pre-empt kernel on linux-based system.
				\item Assembled and tested rover motors and servos
				\item Setup Ardurover on real-time system 
			\end{itemize}
			\textbf{Autonomous Systems Laboratory (UCSC)} \hfill \textbf{September 2017 - Current}\\
			\quad Researcher
			\begin{itemize}[noitemsep,topsep=0pt]
			\item Programmed and tested embedded guidance system in C for an autonomous surface vehicle.
			\item Designed MAVLink interface for path-planning, Gaussian Process Regression (GPR) for spatial estimation during run-time, attitude estimation, and GPS for waypoint-to-waypoint navigation
			\end{itemize}
			\textbf{University of California at Santa Cruz} \hfill \textbf{September 2017 - Current}\\
			\quad Teaching Assistant
			\begin{itemize}[noitemsep,topsep=0pt]
			\item \textbf{Mechatronics} (Fall 2017, 2018, Spring 2019, Fall 2021): Led instructional lab sections teaching students about event-driven programming, hierarchical state machines, sensor design, and system integration. Managed six tutors, and manufacturing of class hardware.
			\item \textbf{Sensor and Sensing Technology} (Winter 2018, 2019) Taught students how to implment and use resistive flex sensors, piezo electric sensors, capacitive touch sensors, gyroscopes, accelerometers, magnetometers as part of an inertial measurements unit. Lectured on attitude estimation using complementary filters and IMU calibration.
			\item \textbf{Embedded Systems and C Programming} (Spring \& Summer 2018, Summer 2019) Topics included: basic syntax, pointers, memory allocation, hardware interrupt sub-routines, debouncing, and basic file IO.
			\item \textbf{Microcontroller System Design} (Fall 2019) Topics included: Interrupt-driven UART, I2C, SPI, packet systems, FIR filters, interfacing with external EEPROM, encoders, an H-Bridge, and interupt-driven PID loops for controlling motor rate and position. 
			\end{itemize}
			\textbf{COSMOS California Summer School for Mathematics \& Science}  \hfill \textbf{Summer 2018}\\
			\quad Tutor
			\begin{itemize}[noitemsep,topsep=0pt]
			\item Taught students state-machine programming in C of small two-wheeled robots with bump-sensors and photo-resistors for shadow-finding.
			\end{itemize}
			\textbf{Inboard Technologies} \hfill \textbf{Summer 2017}\\
			\quad Electrical Engineering Intern
			\begin{itemize}[noitemsep,topsep=0pt]
			\item Designed and implemented test-rig dynamometer for BLDC motors for electric skateboard.
			\item Repaired lithium-ion battery packs
			\item Refurbished battery management systems
			\end{itemize}
		}%
	\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\colorbox{black}{\color{white}{
			\parbox[t]{\leftColWidth}{%
				\textbf{Projects}}
		}%
	}
	& &
	\parbox[t]{\mainColWidth}{%
		\textbf{Ball-Balancing Robot} \hfill \textbf{January 2017 - June 2017}\\
		\quad Senior Design Project
		\begin{itemize}[noitemsep,topsep=0pt]
		\item 5ft tall robot, capable of balancing on top of a large basketball.
		\item Implmented embedded PID position control of BLDC motors with encoders, PID loop for balancing on ball using IMU, and  embedded quaternion library.
		\end{itemize}
%		\textbf{Linear Electromagnetic Rail Accelerator (Rail Gun)} \hfill \textbf{March 2020 - current}\\
%		\quad Personal Project
%		\begin{itemize}[noitemsep,topsep=0pt]
%		\item Designed accelerator support structure, high-energy discharge circuitry
%%		\item Modeled projectile for acceleration control with capacitor bank
%		\item Using LIDAR range finding for projectile/payload position feedback control
%		\end{itemize}
		\textbf{Autonomous Robot} \hfill \textbf{Fall 2015}\\
		\quad Final Project for Mechatronics Class 
		\begin{itemize}[noitemsep,topsep=0pt]
		\item Programmed hierarchical state machine (HSM) in C, based on event-driven programming.
		\item Robot capable of locating ping-pong balls on field, firing balls at opponent robot, and locating safe zone.
		\item Custom made IR, trackwire, bumper, and tape tracking sensors
		\end{itemize}
	}%
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\colorbox{black}{\color{white}{
			\parbox[t]{\leftColWidth}{%
				\textbf{Skills}}
		}%
	}
	& &
	\parbox[t]{\mainColWidth}{%
		\textbf{Software Engineering:} \textbf{Proficient}: C, C++, and Embedded Software Design, \textbf{Competent}: MATLAB, Python, \textbf{Advanced-Beginner}: Simulink, Java \textbf{Novice}: MIPS Assembly\\
		\textbf{Embedded Systems:} \textbf{Proficient}: PIC32, I2C, UART, SPI, NMEA, CAN, sensor integration, Input Capture / Output Compare, Free-Running Timers, Timer Interrupts, ADC, protocol debugging. Discretized PID control loops (non-blocking and interrupt-driven), MAVLink.\\
%		\textbf{Robotics Engineering:} Sensor Fusion, Feedback Control, Sensor Design, Analog Filter Design, Mechatronic Design\\
%		\textbf{Software/Libraries:} \textbf{Proficient}: Mac OS, \textbf{Competent}:Linux/Unix, Windows, Eagle CAD, Solid Works, Fusion 360\\
%		\textbf{Computational \& Applied Mathematics:} Extended Kalman Filters, Control Theory, Digital Control Design, Linear Dynamical Systems, Frequency Domain and State Space Analysis\\
%		\textbf{System Identification:} ARX, ARMAX, Recursive/Weighted Least-Squares (with/without forgetting factor)\\
%	}%
%\\
%% for page break ... until better way is found
%	\colorbox{black}{\color{white}{
%			\parbox[t]{\leftColWidth}{%
%				\textbf{Skills} continued}
%		}%
%	}
%	& & 
%	\parbox[t]{\mainColWidth}{%
		\textbf{Robotics Engineering:} Sensor Fusion, GPS, IMU, Feedback Control, Sensor Design, Analog Filter Design, Mechatronic Design\\
		\textbf{Software/Libraries:} \textbf{Proficient}: Mac OS, \textbf{Competent}: Linux/Unix, Windows, Eagle CAD, Solid Works, Fusion 360\\
		\textbf{Computational \& Applied Mathematics:} Extended Kalman Filters, Control Theory, Digital Control Design, Linear Dynamical Systems, Frequency Domain and State Space Analysis\\
		\textbf{System Identification:} ARX, ARMAX, Recursive/Weighted Least-Squares (with/without forgetting factor)\\
		\textbf{Hardware}: \textbf{Proficient}: Oscilloscopes, Digital Multi-Meters, \textbf{Competent}: Laser Cutters, Logic Analyzers, \textbf{Novice}: 3D Printer, Spectrum Analyzers.
}%
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Honors and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colorbox{black}{\color{white}{
		\parbox[t]{\leftColWidth}{%
			\textbf{Honors \& Awards}}
	}%
}
& &
\parbox[t]{\mainColWidth}{%
	\textbf{Achievement Rewards for College Scientists (ARCS) Foundation Recipient}  \hfill \textbf{Spring 2020}\\
	\quad For academic excellence in studying STEM\\
	\textbf{National I-Corps Program Recommendation}  \hfill \textbf{Spring 2020}\\
	\quad For exemplary performance in I-Corps short course
	\begin{itemize}[noitemsep,topsep=0pt]
	\item Formed small team to interview industry experts to determine the market viability of rail accelerator g-shock testing for custom and off-the-shelf electronics components.
	\item Developed business models, business model canvases, value propositions, and supply chains models.
	\item Identified potential customers, competitors, 
	\end{itemize}
}%
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colorbox{black}{\color{white}{
		\parbox[t]{\leftColWidth}{%
			\textbf{Publications}}
	}%
}
& &
\parbox[t]{\mainColWidth}{%
	\textbf{Low-Cost Validation for Complementary Filter-Based AHRS}  \hfill \textbf{Summer 2020}\\
	\quad 2020 IEEE/ION Position, Location and Navigation Symposium (PLANS)\\
	Developed procedure to validate a complementary filter-based attitude and heading reference system for an off-the-shelf sensor-head using a prototype, low-cost validation apparatus and comparing course over ground measurements from GPS.\\
	\textbf{Partitioned Guassian Process Regression for Online Trajectory Planning for Autonomous Vehicles} \quad \textbf{Summer 2021}\\
	\quad 2021 International Conference on Control and Automation of Systems (ICCAS2021)
	Developed an algorithm to improve the computation time of spatial estimation through ordinary kriging used in online trajecotry planning for an autonomous surface vehicle.
}%
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Volunteer Work
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colorbox{black}{\color{white}{
		\parbox[t]{\leftColWidth}{%
			\textbf{Volunteer Work}}
	}%
}
& &
\parbox[t]{\mainColWidth}{%
	\textbf{Google Summer of Code (GSoC) Mentor}  \hfill \textbf{Summer 2021}\\
	Mentored international students on an IMU calibration and attitude estimation project for an open-source collaboration. \\
	\textbf{UCSC Mechatronics Robot Manufacturing}  \hfill \textbf{Summer 2016}\\
	Assembled, tested, and repaired small robots for UCSC's Mechatronics class. 
}%
\end{align*}
\end{document}